%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{Overleaf}
\fancyhead[RE,LO]{Guides and tutorials}
\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}

 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Suyog}{Jadhav}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.28\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT (ISM), Dhanbad}
\descript{BTech in Electronics and Communication}
\location{May 2021 | Dhanbad (JH), India}
\location{ Cum. GPA: 8.19 / 10.0
% \\ Major GPA: -- / 10.0
}
\sectionsep

\subsection{Modern College, Pune}
\location{Grad. May 2017 |  Pune (MH), India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\href{mailto:suyog.jadhav1@gmail.com}{\bf Mail} \\
\href{http://suyogjadhav.com}{\bf Website} \\
\href{https://scholar.google.com/citations?user=8wS71BQAAAAJ&hl=en}{\bf Google Scholar Profile} \\
\href{https://www.suyogjadhav.com/resume/}{\textbf{Complete Unabridged Resume}}

\sectionsep
Github:// \href{https://github.com/IAmSuyogJadhav}{\bf IAmSuyogJadhav} \\
LinkedIn://  \href{https://www.linkedin.com/in/IAmSuyogJadhav}{\bf IAmSuyogJadhav} \\
Twitter://  \href{https://twitter.com/IAmSuyogJadhav}{\bf IAmSuyogJadhav} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Skills}
\subsection{Programming}
\location{Very Familiar:}
Python \textbullet{} PyTorch \textbullet{} API and backend development (Flask) \textbullet{} Linux \textbullet{} Git \textbullet{} Google Cloud Platform

\location{Over 1000 lines of code:}
C \textbullet{} C++ \textbullet{}  Matlab \textbullet{} Regex \textbullet{} CSS \textbullet{} Keras \textbullet{} TensorFlow

\location{Familiar:}
Shell \textbullet{} Javascript \textbullet{} Batch

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 

\descript{Gold Medal | Dec 2019}
\location{Ashoka's Tech for Change Challenge at 6\textsuperscript{th} Inter-IIT Tech Meet}
\sectionsep
\descript{2\textsuperscript{nd}/150 teams | Sep 2019}
\location{CDAC AI Hackathon 2019 sponsored by Nvidia}
\sectionsep
\descript{4\textsuperscript{th}/300 teams | Jan 2019}
\location{PanIIT Mission AI: Solve for India Hackathon}
\sectionsep
\descript{Rank 6664\textsuperscript{th}/12M | May 2017}
\location{All India Rank in JEE (Advanced) 2017}


% \begin{tabular}{rll}
% 2019	     & Gold Medal  & Ashoka's Tech for Change Challenge \\ & & at Inter-IIT Tech Meet 2019 \\
% 2019         & 2\textsuperscript{nd}/150 teams & CDAC AI Hackathon 2019 sponsored by Nvidia \\
% 2019         & 4\textsuperscript{th}/300 teams & PanIIT Mission AI: Solve for India Hackathon

% \end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.7\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{UiT- The Arctic University of Norway}
\descript{| Research Intern }
\location{Apr 2020 - Aug 2020 | Tromsø, Norway}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{Worked on two different projects during the course of this internship.}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Application of deep learning for illumination estimation in Fourier ptychography microscopy (FPM); manuscript submitted to the Optics Express journal.
\item Artefact removal from MUSICAL nanoscopy images using deep learning; manuscript submitted to the Neural Networks journal.
\end{tightemize}
% Both the projects have been discussed in more detail under the \textit{Research} section. 
\sectionsep

\runsubsection{Cancer Moonshot Inc.}
\descript{| Deep Learning R\&D Intern }
\location{Jun 2019 – Jul 2019 | Bangalore (KA), India}
\location{Worked on developing deep learning models for detection and segmentation of prostate cancer legions from the prostate MRI scans.}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Trained UNet model with some modifications to fit the extremely small ground truth labels. The dataset used was very small, I used data augmentation to increase the effective dataset size and improve the performance of the model. 
\end{tightemize}
\sectionsep

% \runsubsection{DataProrrisi Inc.}
% \descript{| Software Engineering Intern }
% \location{Dec 2018 – Jan 2019 | Remote}
% \begin{tightemize}
% \item Assisted in developing the backend for DataProrrisi, a startup focused on revolutionizing the loan acquisition process using machine learning, based in California.
% \item I used Flask for implementing the necessary API calls needed by the backend.
% \end{tightemize}
% \sectionsep

\runsubsection{Cyber Labs - IIT (ISM) Dhanbad} %- The Arctic University of Norway}
\descript{| AI Team Leader}
\location{Jul 2019 - Present | Dhanbad (JH), India}
\begin{tightemize}
\item My team works on various projects that utilise machine learning. We also conduct workshops, hold paper reading sessions and organize machine learning competitions in the college.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Past Research Projects}

\runsubsection{Artefact Removal from Nanoscopy Images}
% \descript{ }
\descript{| Aug 2020}
MUSICAL is a nanoscopy method that produces a high-res output from a temporal stack of fluorescence microscopy images. Due to the noise in the data, the produced MUSICAL image has background debris and reduced resolvability. I worked on simulating 3 different structures (actins, vesicles and mitochondria) and training autoencoder models for denoising the MUSICAL images. Various loss functions were explored and their performance was evaluated. Under the guidance of \href{https://sites.google.com/site/uthkrishth/krishnaagarwal}{\bf Dr. Krishna Agarwal} and \href{https://sites.google.com/site/dilipprasad/}{\bf Dr. Dilip K. Prasad}.
\sectionsep

\runsubsection{Deep Learning in Fourier Ptychography}
% \descript{ }
\descript{| Jun 2020}
Fourier ptychography is a microscopy technique that uses low-resolution images taken from multiple illumination angles to generate a high-resolution image. I implemented the complete pipeline including the illumination angle estimation model, automatic calibration algorithm, and the final reconstruction algorithm adapted from Aidukas et. al. 2018. For illumination estimation, I trained an object detection model to locate the "pupil" in the Fourier spectra of the input images to estimate the illumination. Under the guidance of \href{https://sites.google.com/site/uthkrishth/krishnaagarwal}{\bf Dr. Krishna Agarwal} and \href{https://sites.google.com/site/dilipprasad/}{\bf Dr. Dilip K. Prasad}.
\sectionsep

% \runsubsection{Deep Learning in Fourier Ptychography}
% \descript{ }
\descript{$\mapsto$ Details about more projects can be found on  \href{https://github.com/IAmSuyogJadhav}{\bf my GitHub profile}}
\sectionsep


% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
